Verifying Demonstrations

### 2019-02-21 paper/protocol.tex
renames subsections, edits for simplification

We now present \CROCUS, a protocol for privately verifiable crowd counts.
The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
join, participation, submission (all in in \cref{ProtocolDuring}) and
verification (in \cref{ProtocolVerification}).

Several entities are involved in our protocol.
First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
person's identity and a cryptographic key\footnote{%
  This can be implemented using any \ac{CA} that prevents Sybil 
  attacks~\cite{SybilAttack} and ensures a one-to-one mapping between a person 
  and a cryptographic key.
  \Ie for each identity it issues one-and-only-one cryptographic key.
}.
The \ac{CA} is only involved in the setup phase.

Second, a participant is an individual who wants to participate in a given 
protest.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and 
  disseminated it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs to protesters which state that the 
  protester was indeed participating, constructed such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act as
either or both protester and witness.

\subsection{Pre-protest phase}%
\label{ProtocolSetup}

The setup step is only run once and is the same as in Anon-Pass~\cite{AnonPass}.
More precisely, we have simply adapted their description to our notation, but otherwise kept the setting as similar as possible.

@@

The setup and registration steps can be done once and the keys can be reused 
for an arbitrary number of protests.

\subsection{Protest phase}%
\label{ProtocolDuring}

@@

Here is an overview of the protocol.

%\begin{figure}
% \centering
  \small
 % \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
      \pi_{\wid})],\quad \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
      \pi_{\pid})],\quad \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
%  \end{minipage}
%  \caption{%
%     An overview of the Join, Participation and Submission phases of \CROCUS.\@
%     The organizer \(O\) broadcasts the manifesto.
%     The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
%     Finally, both \(P\) and \(W\) submit the proof shares to a
%     permanent storage \(S\). Note that \pid always refers to the
%     protester whose presence is being witnessed.
%   }%
%   \label{fig:ProtocolOverview}
% \end{figure}
\normalsize

\subsection{Post-protest phase}%
\label{ProtocolVerification}

@@

To verify the participation count for a protest \(\prtst\) with identifier 
\(\cid_0\), a verifier must download from the storage system \(\TS\) the set 
\(\pshs_{\cid_0}\) of all \(s_P\) and \(s_W\) tuples containing \(\cid_0\).
Then from \(\pshs_{\cid_0}\), a verifier can build, in succession,
\begin{enumerate*}
\item the valid proof shares \(s_j^{(i)}\) for all matching pairs \((s_P, 
    s_W)\) corresponding to a witness \(i\) and a protester \(j\),
\item the participation proof \(\prf_{j}\) for each protester \(j\),
\item the set \(\prfs_{\prtst}^{\str,\theta}\) of eligible participation proofs 
  for all protesters in \(\prtst\), and finally,
\item the participation count, \ie the cardinality of 
  \(\prfs_\prtst^{\str,\theta}\).
\end{enumerate*}

@@

In the case of trusted witnesses, each such trusted witness must
publish or otherwise inform the 
verifier of which proof shares they have signed, \eg by giving a list of all 
such proof shares or digitally signing each proof share\footnote{%
  To achieve witness privacy in this situation, one could employ a group or 
  ring signature scheme for all trusted witnesses.
  Then one learns that at least one trusted witness must have been there.
}.

Note that, thanks to the \((\str,\theta)\)-eligibility criterion (\cref{DefParticipationCount}), the method of counting is extremely generic, and each verifier can make an independent choice to regulate their trust in the final result, based on their initial trust in the witnesses. In other words, anyone who does the counting can choose the eligibility
criteria (time interval, location, number of regular or trusted
witnesses, who is considered to be a trusted witness) for their own count
and as long as these are published along with the result, anyone can
verify the correctness of the count under those criteria, and potentially question the validity of this choice. Biased or partisan verifiers may be tempted to make extreme choices, but they will have to publish those choices and lose credibility. Reasonable verifiers on the other hand will try to find a good middle-ground that counts all legitimate protesters while being resistant to isolated malicious agents.

>>>>

We now present \CROCUS, a protocol for privately verifiable crowd
counts. A prerequisite for using \CROCUS is a one-to-one mapping of a person's
sybil-proof identity and a cryptographic key, in other words an uncloneable
subscription to one's identity\footnote{%
  Given any \ac{CA} that prevents Sybil 
  attacks~\cite{SybilAttack}, systems such as \cite{clonewars} could
  be used to make sure that for each identity one-and-only-one
  cryptographic key is issued. 
}. Since we assume these properties, we
present only the result of the process of getting anonymous
credentials from a \ac{CA}, in \cref{ProtocolSetup}.

The core of the \CROCUS protocol consists of generating participation
proofs (joining a protest, participating in witnessing, submitting
evidence, all in \cref{ProtocolDuring}) with an overview in \cref{fig:ProtocolOverview}, and then counting and
verification of that count (in \cref{ProtocolVerification}).

% The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
% join, participation, submission (all in in \cref{ProtocolDuring}) and
% verification (in \cref{ProtocolVerification}).

The entities involved in our protocol are participants and (count) verifiers.

A participant is an individual who wants to participate in a given 
protest.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto (at minimum a name) for the protest and 
  disseminated it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs to protesters which state that the 
  protester was indeed participating, constructed such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act as
either or both protester and witness.

After the protest, anyone can count the number of participants (of the protest and the
protocol) and verify anyone else's count given the relevant meta data
(which protest, location, time, and witness parameters used in the
count). We refer to anyone counting or verifying a count as the
verifier.

\subsection{Prerequisite: anonymous credentials}%
\label{ProtocolSetup}

Before Alice can have her participation in any event counted by
\CROCUS, she needs to get an anonymous credential and corresponding
keys. This only needs to be repeated when the credential expires or is
lost, in analogy to a passport in terms of expected intervals. The
keys can be reused for an arbitrary number of protests or, given
careful choices in the PRF used for deriving identifiers, other
services that work with anonymous credentials.

We use the setup and registration phases of Anon-Pass~\cite{AnonPass} for
getting anonymous credentials, adapting only the notation to fit ours. 
%More precisely, we have simply adapted their description to our notation, but otherwise kept the setting as similar as possible.

@@

\subsection{Participation}%
\label{ProtocolDuring}

@@

\begin{figure}
 \centering
 % \small
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
      \pi_{\wid})],\quad \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
      \pi_{\pid})],\quad \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of \CROCUS participation.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submit the proof shares to a
    permanent storage \(S\). Note that \pid  always refers to the
    protester whose presence is being witnessed.
  }%
  \label{fig:ProtocolOverview}
\end{figure}
%\normalsize

\subsection{Count and Verification}%
\label{ProtocolVerification}

@@

To count or verify the participation count for a protest \(\prtst\) with identifier 
\(\cid_0\), a verifier must download from the storage system \(\TS\) the set 
\(\pshs_{\cid_0}\) of all \(s_P\) and \(s_W\) tuples containing \(\cid_0\).
Then from \(\pshs_{\cid_0}\), a verifier can build, in succession,
\begin{enumerate*}
\item the valid proof shares \(s_j^{(i)}\) for all matching pairs \((s_P, 
    s_W)\) corresponding to a witness \(i\) and a protester \(j\),
\item the participation proof \(\prf_{j}\) for each protester \(j\),
\item the set \(\prfs_{\prtst}^{\str,\theta}\) of eligible participation proofs 
  for all protesters in \(\prtst\), and finally,
\item the participation count, \ie the cardinality of 
  \(\prfs_\prtst^{\str,\theta}\).
\end{enumerate*}

@@

In the case of trusted witnesses, each such trusted witness must
publish or otherwise inform the verifier of which proof shares they
have signed, \eg by giving a list of all such proof shares or
digitally signing each proof share\footnote{%
  To achieve witness privacy in this situation, one could employ a
  group or ring signature scheme for a set of trusted witnesses, \eg
  members of an independent journalist association.  Then one learns
  that at least one member of this set of trusted witnesses must have
  been there.  }.

Note that, thanks to the \((\str,\theta)\)-eligibility criterion
(\cref{DefParticipationCount}), the method of counting is extremely
generic, and each (counting) verifier can make an independent choice to regulate their trust in the final result, based on their initial trust in the witnesses. In other words, anyone who does the counting can choose the eligibility
criteria (time interval, location, number of regular or trusted
witnesses, who is considered to be a trusted witness) for their own count
and as long as these are published along with the result, anyone can
verify the correctness of the count under those criteria, and potentially question the validity of this choice. Biased or partisan verifiers may be tempted to make extreme choices, but they will have to publish those choices and lose credibility. Reasonable verifiers on the other hand will try to find a good middle-ground that counts all legitimate protesters while being resistant to isolated malicious agents.
